### 2018-10-09 pilot_manuscript.Rmd
fixed the warriner words

knitr::opts_chunk$set(cache = TRUE)
```
# Introduction

@@

This project brings the two together in holy matrimony.
# Method

@@

###harm
#read in the harm total words from the mtmm project
harm_all = read.csv("harm_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
#table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
#fought, safer, spurn

#Fair
fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
#table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
#fought, safer, spurn

@@

@@

@@

purity_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

>>>>

knitr::opts_chunk$set(cache = TRUE)
```

@@

This project brings the two together in holy matrimony.

# Method

@@

####harm####

#read in the harm total words from the mtmm project
harm_all = read.csv("harm_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
#fought, safer, spurn
harm_final_data$valence[harm_final_data$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
harm_final_data$valence[harm_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
#no spurn avaliable

####Fair####
fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)

@@

fair_final_data$valence = vlookup(fair_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
#just plagiar safer
fair_final_data$valence[fair_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
#nothing for just or plagiarism

@@

ingroup_final_data$valence = vlookup(ingroup_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(ingroup_final_data$Var1[is.na(ingroup_final_data$valence) & ingroup_final_data$Freq > 0])
#backstabb  benedict      best      fals   indvidu      juda    knight      true
ingroup_final_data$valence[ingroup_final_data$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
ingroup_final_data$valence[ingroup_final_data$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
ingroup_final_data$valence[ingroup_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])

@@

authority_final_data$valence = vlookup(authority_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(authority_final_data$Var1[is.na(authority_final_data$valence) & authority_final_data$Freq > 0])
#  abov behind   gase higher  older  taken 
authority_final_data$valence[authority_final_data$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
authority_final_data$valence[authority_final_data$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
authority_final_data$valence[authority_final_data$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
authority_final_data$valence[authority_final_data$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])

@@

purity_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

@@

purity_final_data$valence = vlookup(purity_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(purity_final_data$Var1[is.na(purity_final_data$valence) & purity_final_data$Freq > 0])
#befor christian     jesus      mari      none    sacred    someon      true     women 
purity_final_data$valence[purity_final_data$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
purity_final_data$valence[purity_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
purity_final_data$valence[purity_final_data$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
```
